How economic, health and social factors affect life expectancy in developing countries?

### 2025-04-08 paper.Rmd
added std residual hist for preliminary model

plot(preliminary_model, which = 1)
plot(preliminary_model, which = 2)
standard_residuals = rstandard(preliminary_model)
plot(data_interest$schooling, standard_residuals, main="Standardized Residuals V. Schooling", 
     xlab="Average Years in School", ylab="Standardized Residuals")

>>>>

plot(preliminary_model, which = 1)
# plot(preliminary_model, which = 2)
standard_residuals = rstandard(preliminary_model)
plot(data_interest$schooling, standard_residuals, main="Standardized Residuals V. Schooling", 
     xlab="Average Years in School", ylab="Standardized Residuals")
hist(rstandard(preliminary_model), main="Histogram of Standized Residuals", xlab="Residuals")
